%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{}{ Vu Long }{ \urlstyle{same}\href{https://me.vulong.dev}{me.vulong.dev} | \href{mailto:vulong1602@gmail.com}{vulong1602@gmail.com} | (+65) 88907162}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.3\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Bach Khoa University}
\descript{Bachelor of Engineering }
\location{Control Engineering and Automation}
\location{HCMC  - Vietnam}
\location{Sep 2013 - Apr 2018}
\location{GPA: 8.64 / 10.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/lovung}{\bf lovung} \\
LinkedIn://  \href{https://www.linkedin.com/in/vu-long/}{\bf vu-long} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Golang \textbullet{} C \textbullet{} Dart \textbullet{} Shell \\
Python \textbullet{} JS \textbullet{} Vim \\
\sectionsep
\subsection{Tools}
git \textbullet{}  Docker \textbullet{} Grafana
\sectionsep
\subsection{DB and Persistences}
MySQL \textbullet{}  Redis \textbullet{} Kafka
\sectionsep
\subsection{DevOps}
Gitlab CI \textbullet{} Github Action \textbullet{} \\
Kubernetes \textbullet{} CNCF projects
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\textbullet{} \href{https://github.com/lovung/GoCleanArchitecture}{ Golang clean \\ architecture template } \\
\textbullet{} \href{https://github.com/lovung/date}{ Date library } \\
\textbullet{} \href{https://github.com/lovung/decimal}{ Decimal library } \\
\textbullet{} \href{https://github.com/lovung/challenges}{ Challenges } \\
\textbullet{} \href{https://github.com/lovung/simplify-debts-demo}{ Simplify debts } \\
\textbullet{} \href{https://github.com/lovung/memcache}{ Memcache } \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2020 &  Monthly Hero \\ & Golang course team \\ & MFV \\
2019 & Good Engineer in Year \\ & VinID/OneID \\
2018 & Top 15 - ZAChallenge  \\ & Zalo - VNG \\
2017 & Top 5 Employee of Year \\ & Hubble Connected \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.69\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experiences}
\runsubsection{Shopee}
\descript{| Software Engineer }
\location{Jun 2021 - Present | Singapore}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Migrating \textbf{10+} APIs from Python to Golang also improving the code structure with design pattern, improving the performance to handle  \textbf{500k+} QPS during Campaign.
\item Applied unified caching, saving  \textbf{millions} QPS to call lower layers. Implementing the flexible rate limiter to block \textbf{20k+} spam QPS. 
\item Applied flexible i18n loading to reduce re-deployments.
\item Developing the marketplace features to adapt user behaviors like: Component list, Payment cards, Promotion event sync, etc.
\end{tightemize}
\sectionsep

\runsubsection{Money Forward Vietnam}
\descript{| Senior Backend Engineer }
\location{Jul 2020 – May 2021 | HCMC, Vietnam}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Built the Golang Backend Code structure from \textbf{scratch} with Clean architecture, linter, unit test, and integration test. Defined the git workflow standard, set up CI/CD workflow. 
\item Applied the  \textbf{Bi-temporal} models for Asset Accounting SaaS system. Finished \textbf{3 phases} of product with Deprecation as main feature.
\item Reviewed CVs. Reviewed the coding challenges. Interviewed the candidates.
\end{tightemize}
\sectionsep

\runsubsection{VinID / OneID}
\descript{| Senior Software Engineer then Engineer Manager }
\location{Feb 2019 – Jul 2020 | HCMC, Vietnam}
\begin{tightemize}
\item Built from \textbf{scratch} the backend services by Golang for Merchant Platform (support Merchant site, Merchant app, OPS site, Integration service, etc.).
\item Built from \textbf{scratch} Merchant app (MVP version in \textbf{2 months}) with Flutter framework. This app was working smoothly with multiple modules and multiple teams. It had \textbf{30K+} monthly active users at this moment.
\item Defined the git workflow standard, set up CI/CD workflow (for both App and Backend) to work smoothly and fast. It's referred to use by many other teams.
\item Interviewed the new Flutter engineers and led Flutter engineers. 
\end{tightemize}
\sectionsep

\runsubsection{ZALO - VNG}
\descript{| Software Engineer }
\location{May 2018 – Feb 2019 | HCMC, Vietnam}
\begin{tightemize}
\item Developed the kernel module to capture/monitor networking of the server (like Kubernetes) using C Language.
\item Modified OpenSSH service from server-side to track the developer activities via SSH.
\end{tightemize}
\sectionsep

\runsubsection{Hubble Connected}
\descript{| Firmware Engineer }
\location{Mar 2017 – May 2018 | HCMC, Vietnam}
\begin{tightemize}
\item Developed and maintained streaming audio (\textbf{10k+} sold products), smart home devices (\textbf{5k+} sold products) in the IoT team.
\end{tightemize}
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     RESEARCH
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Social organizations}
\runsubsection{\href{https://www.facebook.com/techXVn}{Project X Vietnam Tech Community}}
\descript{| Mentor}
\location{May 2022 – Present | Worldwide}
A non-profit organization with a vision to create a powerful network that empowers the Vietnamese youths and provides supports to the growing tech startup community.
\sectionsep

% \runsubsection{Cornell Phonetics Lab}
% \descript{| Head Undergraduate Researcher}
% \location{Mar 2012 – May 2013 | Ithaca, NY}
% Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. 
% \sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
